%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{C}
\Huge{Alexander Garcia}\\
\href{tel:+18324518420}{\raisebox{-0.05\height}\faMobile \ 832-451-8420} \\
\href{mailto:alexander.a.garcia94@hotmail.com}{\raisebox{-0.05\height}\faEnvelope \ alexander.a.garcia94@hotmail.com} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------
\section{Keywords}
\begin{tabularx}{\linewidth}{|C|C|}
\textbf{Software Engineer} \ &
\textbf{New Grad} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Objective
%----------------------------------------------------------------------------------------
\section{Objective}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Dedicated and detail-oriented Computer Science graduate seeking an entry-level position in the technology field. \\
Offering a strong foundation in programming, problem-solving, and a passion for learning new skills and strengthening existing skills.
\end{tabularx}



%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{ @{}lCr@{} }
\textbf{Bachelor of Science, Computer Science}  & & GPA 3.60\\
Southern New Hampshire University
\end{tabularx}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages: &  \normalsize{C++, C\#, Python}\\
Frameworks: & \normalsize{Angular, Express, Nodejs}\\
Tools: & \normalsize{Docker, Git, Gitlab, Godot, Unreal, React}\\
Other: & \normalsize{Problem Solver, Strong Work Ethic, Effective Communication, Bilingual\: Spanish}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Project Experience
\section{Projects}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Personal Website} Fall 2023 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Designed and implemented a responsive front-end interface using React.
            \item[--] Developed a robust back-end system with Node.js and MongoDB, enabling seamless data storage and retrieval for blog posts and associated media.
            \item[--] Integrated user authentication to enhance security.
            \item[--] URL: AlexGarcia.fun
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Time Tracking Web App} Winter 2024 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Developed a comprehensive web application using React to aid nurses in efficiently tracking and managing postpartum hemorrhage events.
            \item[--] Collaborated with healthcare professionals to understand their needs and incorporated user feedback for continuous improvement of the application.
            \item[--] Conducted thorough testing and debugging processes to ensure the reliability and accuracy of the application.
            \item[--] URL: PPHTracker.com
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Godot Game} Summer 2022 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Developed a game for a game jam in one week, incorporating diverse mechanics and challenging puzzles.
            \item[--] Programmed the game using the Godot engine and successfully published it online.
            \item[--] The game is available for download at: https://trismister.itch.io/boala-the-koala
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

%Work Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Warehouse Associate}&\textbf{Amazon}&\hfill Most Recent \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Work as part of a team in a fulfillment center, specializing in packing singles and utilizing smart pack machines.
            \item[--] Trained as a problem solver for smart pack kickout, ensuring efficient packaging processes using Amazon computerized systems.
            \item[--] Demonstrated  strong attention to detail in managing packing tasks and maintaining quality standards.
            \item[--] Utilized problem solving skills to troubleshoot issues and contribute to smooth operations.
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Emergency Department Tech}&\textbf{Tenet Healthcare}&\hfill Jul 2010 - Mar 2021 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Performed routine patient care, support, and services under direction from nurses in department.
            \item[--] Integrated education, technical competence, and patient interaction skills to gain confidence and cooperation from the patient.
            \item[--] Exercised sound judgment, and developed clinical skills to support the patient's plan of care based on the diagnosis in a timely manner.
            \item[--] Followed all local/state/federal regulations, codes, policies and procedures to ensure privacy and safety to help deliver optimal patient care.
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
